CTest Integration of Sikuli Automated GUI Testing

### 2011-06-10 Documentation/Article.tex
Updated explanation of Gofigure2 example script

Can you add comments in your example, please?

>>>>

The Sikuli script in Figure 2 shows a unit test for the GoFigure2 software.  The unit being tested here
is the Toolbar menu which consists of different modes used to analyze data set plots, like zoom and pan.
In total there are four modes which are represented in the first line as the vector Toolbar and for each
of these modes we want to test their expected mouse functions.  For instance, if we are in the zoom Toolbar mode
then we would want the data set plot to zoom in when the user scrolls the mouse wheel towards the computer.  Likewise,
if we are in pan mode then we want the plot to move to the left if the user holds down the left mouse button and moves
the mouse to the left.  Also importantly, we want to see that these two mouse actions are unique for their respective Toolbar modes.
The test will include an assertion that scrolling forward will zoom in when using zoom mode and will do nothing when using pan mode.\\

This breakdown of modes and actions lends itself to a nested for-loop scripting approach. In addition to representing the modes and actions
as the vectors Toolbar and Mouse, respectively, we've included the different data set plots in the vector ViewRegion.
These images represent the xy, xz, yz, xyz views of zebrafish microscopy data taken in the Megason Lab.  After capturing
these images we can then use them to locate their initial xy pixel coordinates within the GoFigure2 GUI using the find() function.  These points become 
our reference positions to calculate directional movement.  For example, when testing the pan mode, we mark the initial position of each image,
use the mouseMove() function to a chosen location, and then use find() to obtain the new coordinates.  We can then assert if the image panned as it should have.
Similarly for zoom, we can first find the area of the image and then find the area of the zoomed in image.  To test the result when the user clicks 
in a certain mode, we've made use of Sikuli's assert exists() function to ascertain the existence of our
desired results.        (see Figure~\ref{fig:Gofigure2Example}).
